---
title: "APS Failure in Scania Trucks"
author: "Group 1"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::gitbook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2);
```

## Introduction of Scania Air Pressure system case

The dataset consists of data collected from heavy Scania trucks in everyday usage. The system in focus is the **Air Pressure system (APS)** which generates pressurised air that are utilized in various functions in a truck, such as braking and gear changes.
The data consists of a subset of all available data, selected by experts.
The **positive** class consists of component failures for a specific component of the APS system. 
The **negative** class consists of trucks with failures for components not related to the APS.      
For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

## Data load and cleaning
The data source consist in a csv file that contains many missing vales references as 'na'.
To properly import the information it is needed to identify 'na' as #NA values.


```{r }
#Read file with column headers and force "na" as NA
training_set <- read.csv("aps_failure_training_set.csv", header=TRUE, na.strings="na", stringsAsFactors = FALSE)
head(training_set [1:17], 5)
```


## Data Transformation
It has been identified that when a histogram value is missing all the remaining values are also missing.
```{r }
#if histogram are missing only 4 out of 671 rows are faulty
qplot(as.factor(training_set[is.na(training_set$ag_000),]$class), xlab = "class")

```


```{r , echo=FALSE}
#if histogram are missing only 4 out of 671 rows are faulty
training_set = training_set[!is.na(training_set$ag_000),] 
```


```{r , echo=FALSE}
# visualize class value distributions
qplot(as.factor(training_set$class), xlab = "class")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
